Multiresolution Neural Field Estimation

### 2011-03-02 Multiresolution_framework/ltx/manuscript.tex
update to results

\section{Results}
To demonstrate the performance of the MRA estimation framework, data was generated synthetically  using Eqs.~\ref{eq:DiscreteTimeModel} and \ref{eq:ObservationEquation}, enabling a comparison between true and estimated parameters. 100 realizations of 1 second of data were generated where $\boldsymbol\Sigma_v=0.1 \times \mathbf{I}_{n_y}$ and $\eta(r-r')=\phi_{3,-2}(r-r')$ (\dean{Defining the covariance this way is confusing, just like it was for the sensor kernel. It implies that the disturbance covariance to directly related to the field, or the basis was chosen because of the disturbance. Can we simply say that the disturbance covariance was a b-spline with dilation xx?}). 
The sampling period and the synaptic time constant were set to $T_s = 1$~ms and $\tau = 10$~ms, respectively. The distance between adjacent sensors was $0.5$~mm resulting into 161 observations. \parham{Since $n_x<161$ at each level, this provides enough information for state estiamation due to orthogonality of the basis functions.}  The observation kernel is modeled using a B-spline function, with a width of 0.8~mm at half the maximum amplitude of the observation kernel. The spacing and bandwidth of the sensors allowed for the full spatial bandwidth of the field to be observed. The spatial cutoff frequency of the observed field, $y_t(r_n)$, was used to specify the level of decomposition required to represent the field using the wavelets. The spatial cutoff frequency was \dean{??} cycles/mm. Therefore, wavelets up to level $j=2$ (with the bandwidth $\approx[2.5,4]$ cycles/mm) can represent the significant spatial characteristics of the field. \cut{Note that wavelets due to their bandpass filter characteristics extract successively higher and higher frequency components by increasing $j$.}

Field reconstruction \dean{using the results of the EM algorithm} at different levels of approximations is shown in \figurename{\ref{fig:FieldEstimates}}. \dean{Needs more info. Like that the results are great!} The figure confirms that $j=2$ is adequate to capture the dynamic of the underlying field, where the RMSE . The root mean square error (RMSE) of the field estimates is shown in \figurename{\ref{fig:ParametersHistogram}} (a). 
The actual connectivity kernel and its decomposition are plotted in \figurename{\ref{fig:KernelAndFreqResponse}} (a). 
The histogram in \figurename{\ref{fig:ParametersHistogram}} demonstrates the performance of the parameter estimation. \dean{The results are good because the RMSE between the true and estimated kernels is $1.83$ (units?)... There is a bias of 7.4 \% in $\theta_1$ because..., which is not big deal.}
% \begin{figure}[!h]
%  \centering
%  \includegraphics[scale=.9]{./Graph/ObservationFreqResponse.pdf}
%  \caption{(a) Mexican-hat connectivity kernel. The kernel is a composite of two B-spline
% functions (dashed lines), representing local excitation and lateral inhibition. (b) The average (over time) power in dB of the spatial frequency of the observations. The dashed line shows the cutoff frequency (-3 dB point).}
% \label{fig:KernelAndFreqResponse} 
%   \end{figure} 
\begin{figure}[!h] 
 \centering
 \includegraphics[scale=1]{./Graph/Field.pdf}
 \caption{Actual (black line) and estimated (gray line) neural fields at a time instant for different spatial resolutions. (a) $j=0$, $n_x=17$, RMSE =4.44 . (b) $j=1$, $n_x=33$, RMSE =1.87 . (c) $j=2$, $n_x=65$, RMSE =1.2 . (d) $j=3$, $n_x=131$, RMSE = 1.04 . (e) $j=4$, $n_x=263$, RMSE = 1.04 .}
 \label{fig:FieldEstimates}
 \end{figure} 
% \begin{figure}[!h] 
%  \centering
%  \includegraphics[scale=1]{./Graph/Hist.pdf}
%  \caption{(a) RMSE of the estimated field at different spatial scales. (b-c) Histograms of the excitatory and inhibitory connectivity basis function parameter estimates, $\theta_0$ and $\theta_1$, respectively. The solid lines show the actual parameter values and the dotted lines show the estimated parameters means.}
%  \label{fig:ParametersHistogram}
%  \end{figure} 
\begin{figure}[!h] 
 \centering
 \includegraphics[scale=1]{./Graph/Kernel.pdf}
 \caption{The actual connectivity kernel is shown with the black solid line. The estimated kernel and confidence interval is shown by the red line and red shaded region ($\pm2$ std). The 7 weighted kernel basis functions are shown by the black dashed lines.}
 \label{fig:KernelEstimate}
 \end{figure}

>>>>

\section{Results}
To demonstrate the performance of the MRA estimation framework, data was generated synthetically  using Eqs.~\ref{eq:DiscreteTimeModel} and \ref{eq:ObservationEquation}, enabling a comparison between true and estimated parameters. 100 realizations of 1 second of data were generated where $\boldsymbol\Sigma_v=0.1 \times \mathbf{I}_{n_y}$ and $\eta(r-r')=\phi_{3,-2}(r-r')$ (\dean{Defining the covariance this way is confusing, just like it was for the sensor kernel. It implies that the disturbance covariance to directly related to the field, or the basis was chosen because of the disturbance. Can we simply say that the disturbance covariance was a b-spline with dilation xx?}). 
The sampling period and the synaptic time constant were set to $T_s = 1$~ms and $\tau = 10$~ms, respectively. The distance between adjacent sensors was $0.5$~mm resulting into 161 observations. \parham{Since $n_x<161$ at each level, this provides enough information for state estimation due to orthogonality of the basis functions.}  The observation kernel is modeled using a B-spline function, with a width of 0.8~mm at half the maximum amplitude of the observation kernel. The spacing and bandwidth of the sensors allowed for the full spatial bandwidth of the field to be observed. The spatial cutoff frequency of the observed field, $y_t(r_n)$, was used to specify the level of decomposition required to represent the field using the wavelets. The spatial cutoff frequency was \dean{??} cycles/mm. Therefore, wavelets up to level $j=2$ (with the bandwidth $\approx[2.5,4]$ cycles/mm) can represent the significant spatial characteristics of the field. \cut{Note that wavelets due to their bandpass filter characteristics extract successively higher and higher frequency components by increasing $j$.}

Field reconstruction \dean{using the results of the EM algorithm} at different levels of approximations is shown in \figurename{\ref{fig:FieldEstimates}}. \dean{Needs more info. Like that the results are great!} The figure confirms that $j=2$ is adequate to capture the dynamics of the underlying field, where the RMSE converges to a steady value of \dean{xx}. \dean{j=3 seems like where it converges?} The actual connectivity kernel and the decomposition is plotted in \figurename{\ref{fig:KernelEstimate}}. \dean{The results are good because the RMSE between the true and estimated kernels is $1.83$ (units?)... There is a bias of 7.4 \% in $\theta_1$ because..., which is not big deal.}
% \begin{figure}[!h]
%  \centering
%  \includegraphics[scale=.9]{./Graph/ObservationFreqResponse.pdf}
%  \caption{(a) Mexican-hat connectivity kernel. The kernel is a composite of two B-spline
% functions (dashed lines), representing local excitation and lateral inhibition. (b) The average (over time) power in dB of the spatial frequency of the observations. The dashed line shows the cutoff frequency (-3 dB point).}
% \label{fig:KernelAndFreqResponse} 
%   \end{figure} 
\begin{figure}[!h] 
 \centering
 \includegraphics[scale=1]{./Graph/Field.pdf}
 \caption{Actual (black line) and estimated (gray line) neural fields at a time instant for different spatial resolutions. (a) $j=0$, $n_x=17$, RMSE =4.44 . (b) $j=1$, $n_x=33$, RMSE =1.87 . (c) $j=2$, $n_x=65$, RMSE =1.2 . (d) $j=3$, $n_x=131$, RMSE = 1.04 . (e) $j=4$, $n_x=263$, RMSE = 1.04 .}
 \label{fig:FieldEstimates}
 \end{figure} 
% \begin{figure}[!h] 
%  \centering
%  \includegraphics[scale=1]{./Graph/Hist.pdf}
%  \caption{(a) RMSE of the estimated field at different spatial scales. (b-c) Histograms of the excitatory and inhibitory connectivity basis function parameter estimates, $\theta_0$ and $\theta_1$, respectively. The solid lines show the actual parameter values and the dotted lines show the estimated parameters means.}
%  \label{fig:ParametersHistogram}
%  \end{figure} 
\begin{figure}[!h] 
 \centering
 \includegraphics[scale=1]{./Graph/Kernel.pdf}
 \caption{The actual connectivity kernel is shown with the black solid line. The estimated kernel and confidence interval is shown by the red line and red shaded region ($\pm2$ std). The 7 weighted kernel basis functions are shown by the black dashed lines.}
 \label{fig:KernelEstimate}
 \end{figure}
